\chapter{A Grand Apparatus}
\section{The Large Hadron Collider}
% Give some history
%    - collider physics + others? (i.e. ...so we bury enormous colliders underground, still others position enormous film cameras to...)
%    - Some pictures of groundbreaking?
%    - LEP?
%    - Some impressive plots/pictures (e.g. arial shot, of course)
The purpose of this page is to illustrate an ordinary page of text in
a doctoral dissertation or master's thesis. All pages of the doctoral
dissertation or master's thesis must be kept within the margins of
1.5'' on the left, 1'' on the right, 1'' on the top and 1.25'' on the
bottom. All text must be double spaced except as indicated below.

It is recommended that to increase the margins as paper can shift in a
printer and as some photocopiers tend to increase the image being
copied.

The first line of each paragraph must be indented at least one 0.5''
tab, as done here.

This text is intended to be a part of the dissertation, for a doctoral
student, or the thesis if you are receiving a master's degree, and now
a quote is included here:
\begin{quote}
All quotes of more than six lines, even though this one is not, are to
be indented 0.5'' from the left and 0.5'' from the right. These longer
quotes are to be single spaced. Don't forget to adjust for proper
spacing after the last line of the quoted material.
\end{quote}
The rest of the paragraph would continue as so.
\section{The Compact Muon Solenoid}
% Overview: "Compact" "Muon" "Solenoid"?
%    - i.e. what is it supposed to do?
%    - show diagram from UChicago proposal of the generalized particle layers
% Explain each layer
%    - mention russia shells --> calorimeter
\section{The High Lumonisity Era}
% What is HL?
%    - show pileup plots, maybe side AND 3D volume
% What benefits does it bring?
%    - Find some papers...
% What challenges does it bring?
%    - Show CPU/Data volume plots
